%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {IT - Network \& Hardware Technologies} % Job title
    {Peano} % Organization
    {Ottawa \& Montreal, Canada} % Location
    {May 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design, deploy, and maintain websites for our businesses.}
        \item {Respond to user requests for service, troubleshoot problems and help develop solutions.}
        \item {Support PC hardware components, desktop operating system software, and application software.}
        \item {Perform minor repairs to equipment and arrange for other servicing needs.}
        \item {Identify and report system issues to vendors. Monitor and test resolution of those issues sent to vendors.}
        \item {Monitor antivirus software and updates, and repair computers infected with spyware, adware and/or viruses. Monitor backup systems and procedures to ensure data security.}
        \item {Record activities, solutions, and other responses to request for service.}
        \item {Contribute to technical documentation and participate in policy, procedure, and standards development. Assist in maintaining inventory records and documentation for equipment.}
        \item {Consult with vendors, perform research, and evaluate products to assist in the selection and purchase of equipment and installation or upgrade of systems.}
        \item {Develop and provide user training for basic hardware and software use.}
        \item {Provide backup technical support for network including router, firewall, and wireless access point.}
        \item {Perform other duties/projects as assigned.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Design \& Computer/Network Technician} % Job title
    {Self-employment} % Organization
    {Ottawa, Canada} % Location
    {May 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design, deploy, and maintain websites for small businesses and individuals.}
        \item {Optimize and expand home networks.}
        \item {Build computers according to the clients' needs and budget.}
        \item {Conduct hardware and software troubleshooting to repair and maximize the performance of computers.}
        \item {Write articles on technology topics of interest (security, decentralization, innovation, …)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Technician | High School Co-op} % Job title
    {Farm Boy} % Organization
    {Ottawa, Canada} % Location
    {Mar. 2018 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Repair and upgrade computers, Macs, phones, and laptops.}
        \item {Set up phones, laptops, and workstations for staff.}
        \item {Ensure that inventory is properly maintained.}
        \item {Learn about scripting and networking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
